COG-ED Manuscript

### 2022-01-05 06_Paper/COG-ED/Manuscript.Rmd
started adding Bayes factors

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models

@@

@@

@@

@@

@@

@@

  # H3a: Subjective values predict individual NCS scores.

@@

  # H3b: NASA-TLX scores do not predict individual NCS scores.

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package

@@

  # get Bayes factor

  hypothesis1a_BF <- anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)

@@

  # get Bayes factor

  hypothesis1b_BF <- anovaBF(formula = medianrt ~ level, data = h1b_data, progress = FALSE)

@@

  for (i in c(1:5,7:(length(setindex)-1))) { # we exclude the sixth subject (ID F30T02) here, because their NTLX data for n = 1 is missing

@@

  # get Bayes factors

  hypothesis1c_mental_BF <- anovaBF(formula = mental ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_physical_BF <- anovaBF(formula = physical ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_time_BF <- anovaBF(formula = time ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_performance_BF <- anovaBF(formula = performance ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_effort_BF <- anovaBF(formula = effort ~ level, data = h1c_data, progress = FALSE)
  hypothesis1c_frustration_BF <- anovaBF(formula = frustration ~ level, data = h1c_data, progress = FALSE)

@@

  # get Bayes factor

  hypothesis2a_BF <- anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)

@@

  # H3a: Subjective values positively predict individual NCS scores.

@@

  # H3b: NASA-TLX scores negatively predict individual NCS scores.
